---
title: "new.zealand.map2"
output: html_document
---

```{r}
f <- "/Users/karimprimov/Desktop/UT Austin/Applied Data Analysis/data.visualization.project/stolenvehicles.csv"
d <- read_csv(f, col_names = TRUE)
```


```{r}
# Add fill layer to nz shape
tm_shape(nz) +
  tm_fill() 
# Add border layer to nz shape
tm_shape(nz) +
  tm_borders() 
# Add fill and border layers to nz shape
tm_shape(nz) +
  tm_fill() +
  tm_borders() 
```

```{r}
map_nz = tm_shape(nz) + tm_polygons()
class(map_nz)
```

```{r}
map_nz$tm_shape$shp$Name
```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```


# map_nz1 = map_nz +
#   tm_shape(nz_elev) + tm_raster(alpha = 0.7)
# 
# nz_water = st_union(nz) %>% st_buffer(22200) %>% 
#   st_cast(to = "LINESTRING")
# map_nz2 = map_nz1 +
#   tm_shape(nz_water) + tm_lines()
# 
# map_nz3 = map_nz2 +
#   tm_shape(nz_height) + tm_dots()
# 
# tmap_arrange(map_nz1, map_nz2, map_nz3)
# 
# 
# ma1 = tm_shape(nz) + tm_fill(col = "red")
# ma2 = tm_shape(nz) + tm_fill(col = "red", alpha = 0.3)
# ma3 = tm_shape(nz) + tm_borders(col = "blue")
# ma4 = tm_shape(nz) + tm_borders(lwd = 3)
# ma5 = tm_shape(nz) + tm_borders(lty = 2)
# ma6 = tm_shape(nz) + tm_fill(col = "red", alpha = 0.3) +
#   tm_borders(col = "blue", lwd = 3, lty = 2)
# tmap_arrange(ma1, ma2, ma3, ma4, ma5, ma6)
# 
# plot(st_geometry(nz), col = nz$Land_area)  # works
# tm_shape(nz) + tm_fill(col = nz$Land_area) # fails
# #> Error: Fill argument neither colors nor valid variable name(s)
# 
# tm_shape(nz) + tm_fill(col = "Land_area")
# 
# 
# legend_title = expression("Area (km"^2*")")
# map_nza = tm_shape(nz) +
#   tm_fill(col = "Land_area", title = legend_title) + tm_borders()
# 
# tm_shape(nz) + tm_polygons(col = "Median_income")
# breaks = c(0, 3, 4, 5) * 10000
# tm_shape(nz) + tm_polygons(col = "Median_income", breaks = breaks)
# tm_shape(nz) + tm_polygons(col = "Median_income", n = 10)
# tm_shape(nz) + tm_polygons(col = "Median_income", palette = "BuGn")
# 
# 
# tm_shape(nz) + tm_polygons("Population", palette = "Blues")
# tm_shape(nz) + tm_polygons("Population", palette = "YlOrBr")
 